%-------------------------
% Resume in Latex
% Author : Sidratul Muntaha Ahmed
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
      \textbf{\Huge \scshape \href{https://jovanmilicev.com}{Jovan Milicev}} \\ \vspace{0.1in}
    \href{mailto:contact@jovanmilicev.com}{\underline{contact@jovanmilicev.com}} $|$
    \href{https:\\in.jovanmilicev.com}{\underline{in.jovanmilicev.com}} $|$
    \href{https:\\github.jovanmilicev.com}{\underline{github.jovanmilicev.com}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {York University}{April 2023}
      {Honours BA, Computer Science}{Toronto, ON}
          \resumeItemListStart
            \resumeItem{GPA: 3.8 | Data Structures and Algorithms, Computer Architecture, Advanced Object Oriented Programming, Computer Networking, Distributed Systems, Database Management Systems.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

  %-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\href{https://chatbase.co}{Full Stack Developer}}{May 2023 – Present}
      {Chatbase}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Created comprehensive documentation for the Chatbase API, providing clear instructions and guidelines for integration and usage by external developers.}
        \resumeItem{Conducted thorough testing of the API using tools like Postman, ensuring its functionality, reliability, and compatibility with various platforms.}
        \resumeItem{Identified and reported API bugs, providing detailed feedback to the API development team for prompt resolution and improvement of the Chatbase API performance.}
        \resumeItem{Developed a Discord Bot for the platform enabling users to interact with the service through discord.}
      \resumeItemListEnd
    
    \resumeSubheading
      {\href{https://www.yorku.ca/}{Undergraduate Teaching Assistant}}{September 2022 - January 2023}
      {York University}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Teaching assistant for EECS2021 (Computer Organization). Taught basics of assembly language programming in RISC-V and fundamentals of computer architecture in iVerilog.}
        \resumeItem{Facilitated a lab with over 50 students which included solving complex problems, grading assignments, etc. which resulted in an overall increase in the class average.}
        \resumeItem{Graded assignments and exams, providing detailed feedback to students to help them improve their performance and understanding of the course material.}
        \resumeItem{Provided one-on-one tutoring to students who needed extra help, resulting in increased confidence and better academic performance.}
      \resumeItemListEnd
      
    \resumeSubheading
      {\href{https://www.scotiabank.com/ca/en/personal.html}{Customer Experience Associate}}{April 2022 – Present}
      {Scotiabank}{Mississauga, ON}
      \resumeItemListStart
        \resumeItem{Maximized customer satisfaction by helping clients with their banking transactions with a high attention to detail; daily functions included creating bank drafts, mortgage payouts, loan payments, etc.}
        \resumeItem{Identified customer concerns and prioritize customer complaints to the management team to ensure compliance with bank’s policy and improve the overall client experience.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}

    \resumeSubHeadingListStart

        \resumeProjectHeading
            {\textbf{{\href{https://jovanmilicev.com}{Portfolio Webpage}}} $|$ \emph{React, JS}}{May 2023}
            \resumeItemListStart
                \resumeItem{Developed a dynamic and visually appealing portfolio website using React.js, featuring personal projects, skills, and experience to showcase to potential clients and employers.}
                \resumeItem{Continuously updated and maintained the website, adding new projects and improving functionality to enhance user experience and showcase new skills and experience.}
            \resumeItemListEnd
        
        
        \resumeProjectHeading
            {\textbf{{\href{https://jovanmilicev.com/gpt-website}{Querus GPT Website}}} $|$ \emph{Next, JS, Node}}{April 2023}
            \resumeItemListStart
                \resumeItem{Developed a React website that allows users to interact with OpenAI language models.}
                \resumeItem{Used my own node package openai-toolkit to handle API calls to the OpenAI service.}
                \resumeItem{Allows users to configure their spending in tokens and the creativity of the model.}
            \resumeItemListEnd
        
                
          
    \resumeProjectHeading
          {\textbf{Novel Programming Language} $|$ \emph{ANTLR4, Java}}{November 2022 - January 2023}
          \resumeItemListStart
            \resumeItem{Developed a novel programming language using the ANTLR4 parser and Java.}
            \resumeItem{Language capable of performing variable declarations, assignment, math operations and boolean operations.}
            \resumeItem{Includes a simplified JUnit style test suite with branch coverage and other testing statistics.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd





%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, Java, Python, C, GO.} \\
     \textbf{Competencies}{: NodeJS, React/Next.js, Restful APIs, Docker, OOP, Kubernetes, Spark, MongoDB.} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
